moderated_regressions

### 2024-05-01 moderated_regressions.Rmd
updating tables

cr_burn_m1 <- lm(burnout ~ overall.challenge_center, data = data)
summary(cr_burn_m1)

cr_burn_m2 <- lm(burnout ~ overall.challenge_center + overall.resource, data = data)
summary(cr_burn_m2)

cr_burn_m3 <- lm(burnout ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(cr_burn_m3)

aov_test <- anova(cr_burn_m2, cr_burn_m3)
```

@@

cr_stress_m1 <- lm(stress ~ overall.challenge_center, data = data)
summary(cr_stress_m1)

cr_stress_m2 <- lm(stress ~ overall.challenge_center + overall.resource_center, data = data)
summary(cr_stress_m2)

cr_stress_m3 <- lm(stress ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(cr_stress_m3)

anova(cr_stress_m2, cr_stress_m3)
```

@@

cr_eng_m1 <- lm(engagement ~ overall.challenge_center, data = data)
summary(cr_eng_m1)

cr_eng_m2 <- lm(engagement ~ overall.challenge_center + overall.resource_center, data = data)
summary(cr_eng_m2)

cr_eng_m3 <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(cr_eng_m3)

anova(cr_eng_m2, cr_eng_m3)
```

@@

hr_burn_m1 <- lm(burnout ~ overall.hindrance_center, data = data)
summary(hr_burn_m1)

hr_burn_m2 <- lm(burnout ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hr_burn_m2)

hr_burn_m3 <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_burn_m3)

anova(hr_burn_m2, hr_burn_m3)
```

@@

hr_stress_m1 <- lm(stress ~ overall.hindrance_center, data = data)
summary(hr_stress_m1)

hr_stress_m2 <- lm(stress ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hr_stress_m2)

hr_stress_m3 <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_stress_m3)

anova(hr_stress_m2, hr_stress_m3)
```

@@

hr_eng_m1 <- lm(engagement ~ overall.hindrance_center, data = data)
summary(hr_eng_m1)

hr_eng_m2 <- lm(engagement ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hr_eng_m2)

hr_eng_m3 <- lm(engagement ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_eng_m3)

anova(hr_eng_m2, hr_eng_m3)
```

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
b <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
R2 <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
DeltaR <- c("",paste(cr_eng_m2_r),cr_eng_r_square_change, "",paste(cr_stress_m2_r),cr_stress_r_square_change, "",paste(cr_burn_m2_r),cr_burn_r_square_change)

regtable <- cbind(DV, Step, Model, b, R2, DeltaR)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
b <- c(hind.2.eng, res.2hr.eng, int.hr.3.eng, hind.2.stress, res.2hr.stress, int.hr.3.stress, hind.2.burn, res.2hr.burn, int.hr.3.burn)
R2 <- c("", hr_eng_m2_r, hr_eng_m3_r, "", hr_stress_m2_r, hr_stress_m3_r, "", hr_burn_m2_r, hr_burn_m3_r)
DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)

regtable <- cbind(DV, Step, Model, b, R2, DeltaR)

>>>>

cr_burn_m1 <- lm(scale(burnout) ~ scale(overall.challenge_center), data = data)
summary(cr_burn_m1)

cr_burn_m2 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource), data = data)
summary(cr_burn_m2)

cr_burn_m3 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
summary(cr_burn_m3)

aov_test <- anova(cr_burn_m2, cr_burn_m3)
aov_test
```

@@

cr_stress_m1 <- lm(scale(stress) ~ scale(overall.challenge_center), data = data)
summary(cr_stress_m1)

cr_stress_m2 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center), data = data)
summary(cr_stress_m2)

cr_stress_m3 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
summary(cr_stress_m3)

cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
cr_stress_anova
```

@@

cr_eng_m1 <- lm(scale(engagement) ~ scale(overall.challenge_center), data = data)
summary(cr_eng_m1)

cr_eng_m2 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), data = data)
summary(cr_eng_m2)

cr_eng_m3 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
summary(cr_eng_m3)

cr_eng_anova <- anova(cr_eng_m2, cr_eng_m3)
cr_eng_anova
```

@@

hr_burn_m1 <- lm(scale(burnout) ~ scale(overall.hindrance_center), data = data)
summary(hr_burn_m1)

hr_burn_m2 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
summary(hr_burn_m2)

hr_burn_m3 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
summary(hr_burn_m3)

hr_burn_anova <- anova(hr_burn_m2, hr_burn_m3)
hr_burn_anova
```

@@

hr_stress_m1 <- lm(scale(stress) ~ scale(overall.hindrance_center), data = data)
summary(hr_stress_m1)

hr_stress_m2 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
summary(hr_stress_m2)

hr_stress_m3 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
summary(hr_stress_m3)

hr_stress_anova <- anova(hr_stress_m2, hr_stress_m3)
hr_stress_anova
```

@@

hr_eng_m1 <- lm(scale(engagement) ~ scale(overall.hindrance_center), data = data)
summary(hr_eng_m1)

hr_eng_m2 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
summary(hr_eng_m2)

hr_eng_m3 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
summary(hr_eng_m3)

hr_eng_anova <- anova(hr_eng_m2, hr_eng_m3)
hr_eng_anova
```

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
R <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
DeltaR <- c("","",cr_eng_r_square_change, "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

regtable <- cbind(DV, Step, Model, Beta, R, DeltaR)
papaja::apa_table(regtable)
```

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
Beta <- c(hind.2.eng, res.2hr.eng, int.hr.3.eng, hind.2.stress, res.2hr.stress, int.hr.3.stress, hind.2.burn, res.2hr.burn, int.hr.3.burn)
R2 <- c("", hr_eng_m2_r, hr_eng_m3_r, "", hr_stress_m2_r, hr_stress_m3_r, "", hr_burn_m2_r, hr_burn_m3_r)
#DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
DeltaR <- c("","",hr_eng_r_square_change, "","",hr_stress_r_square_change, "","",hr_burn_r_square_change)
regtable <- cbind(DV, Step, Model, Beta, R2, DeltaR)
